Hypertension and microbiome

### 2019-01-25 rrbiome.Rmd
Minor

```{r adonis3}
adonis.species %>%
    data.table::rbindlist(id = "model_name") %>%
#    dplyr::filter(term %in% c("SY) %>%
 #   dplyr::select(-term) %>%
    select(response, SumsOfSqs, MeanSqs, F.Model, R2, "Pr(>F)") %>%
    kable(.)
```

>>>>

```{r adonis3}
adonis.species$max %>%
    data.table::rbindlist(id = "model_name") %>%
#    dplyr::filter(term %in% c("SY) %>%
 #   dplyr::select(-term) %>%
    select(response, SumsOfSqs, MeanSqs, F.Model, R2, "Pr(>F)") %>%
    kable(.)
```
